---
title: "Norton Sound management packet"
format: html
editor: visual
toc: true
---

# Data source

This management packet pulls data directly from the files contained in "Q:\\Salmon\\COMMERCIAL-salmon" and "Q:\\Salmon\\ESCAPEMENT- Salmon".

Historical data is used to calculate escapement and harvest metric quartiles and the current year is not included in these calculations.

For pink salmon, only even or odd year data is used to calculate quartiles depending on the current year.

```{r}
#| label: Start up
#| message: false
#| warning: false
#| include: false
# Start up ####

# Load packages
library(tidyverse)
library(readxl)
library(dplyr)
library(zoo)
library(scales)

# Set current year
yr <- 2026

# Remove scientific notation from plots
options(scipen = 999)
```

```{r}
#| label: Import escapement data
#| message: false
#| warning: false
#| include: false

## Import escapement data ####

## Load data set 

for (file in list.files(path = paste0('Q:/Salmon/ESCAPEMENT- Salmon/', yr, ' Salmon Escapements'),
                        pattern = '\\.xlsx$', full.names = T)) {
  
  # Get available sheets in the current file to prevent errors
  available_sheets <- excel_sheets(file)
  
  for (sheet in c('KING', 'CHUM', 'SOCKEYE', 'RED', 'PINK', 'COHO')) {
    
    # Check if the specific sheet actually exists in this file
    if (sheet %in% available_sheets) {
      
      # Create a clean, unique variable name (e.g., "df_file1_Sheet1")
      to_remove <- c('.xlsx', 'Weir', 'Tower', 'River', yr)
      pattern_regex <- str_c(to_remove, collapse = '|')
      clean_file_name <- str_remove_all(basename(file), pattern_regex)
      var_name <- paste0(clean_file_name, '_', sheet)
      
      # Read the sheet and assign it to its own data frame
      assign(paste0(var_name), read_excel(file, sheet = sheet))
    }
  }
}

# Make a list of data frame names to use for functions 
df_names_esc <- ls(pattern = '^(Pil|Sna|Nom|Eld|Niu|Kwi|Ung|Sha|Nor)', envir = .GlobalEnv)
```

```{r}
#| label: Format esc data
#| message: false
#| warning: false
#| include: false

## Format escapement data ####

esc_format <- function(df) {
  esc_current <- df %>% 
    select(where(~ any(str_detect(as.character(.), "Date"), na.rm = TRUE) ||
                   any(.x %in% 1981:2026, na.rm = TRUE))) %>% 
    slice((which(.data[[names(.)[1]]] == "Date")[1]):nrow(df)) %>% 
    select(!which(duplicated(unlist(slice(., 1))))) %>% 
    set_names(as.character(.[1,])) %>% # Set column names
    slice(-1) %>% # Get rid of redundant top row
    filter(grepl("^\\d{5}$", .[[1]])) %>% 
    mutate(across(-1, as.double)) %>% # Make sure everything is numeric
    mutate(Date = as.Date(as.numeric(Date), origin = '1899-12-30')) %>%  # Repair date
    pivot_longer(cols = !'Date',
                 names_to = 'year',
                 values_to = 'esc') %>% # Long data
    mutate(date = make_date(year, month(Date), day(Date))) %>% # Make yyyy-mm-dd col
    select(-Date) %>% # Get rid of redundant col
    arrange(date) %>% 
    group_by(year) %>% 
    mutate(cum_esc = cumsum(replace_na(esc, 0))) %>% # Calculate yearly cumulative escapement
    ungroup() %>% 
    mutate(day_of_year= format(date, "%m-%d")) %>% 
    select(-year) %>% 
    filter(year(date) == yr)
  
  esc_hist <- df %>% 
    select(where(~ any(str_detect(as.character(.), "Date"), na.rm = TRUE) ||
                   any(.x %in% 1981:2026, na.rm = TRUE))) %>% 
    slice((which(.data[[names(.)[1]]] == "Date")[1]):nrow(df)) %>% 
    select(!which(duplicated(unlist(slice(., 1))))) %>% 
    set_names(as.character(.[1,])) %>% # Set column names
    slice(-1) %>% # Get rid of redundant top row
    filter(grepl("^\\d{5}$", .[[1]])) %>% 
    mutate(across(-1, as.double)) %>% # Make sure everything is numeric
    mutate(Date = as.Date(as.numeric(Date), origin = '1899-12-30')) %>%  # Repair date
    pivot_longer(cols = !'Date',
                 names_to = 'year',
                 values_to = 'esc') %>% # Long data
    mutate(date = make_date(year, month(Date), day(Date))) %>% # Make yyyy-mm-dd col
    select(-Date) %>% # Get rid of redundant col
    arrange(date) %>% 
    group_by(year) %>% 
    mutate(cum_esc = cumsum(replace_na(esc, 0))) %>% # Calculate yearly cumulative escapement
    ungroup() %>% 
    # This if/else filter will use even/odd years for pinks depending on current year ('yr')
    filter(if(grepl('PINK', deparse(substitute(df))) == TRUE) { 
      year(date) %% 2 == yr %% 2
    } else { TRUE }) %>%
    filter(year(date) < yr) %>% 
    group_by(day_of_year = format(date, "%m-%d")) %>%
    # mutate() adds the new columns while keeping all original rows
    mutate(avg_esc = mean(esc, na.rm = TRUE),
           q25 = quantile(esc, probs = 0.25, na.rm = TRUE),
           q50 = quantile(esc, probs = 0.50, na.rm = TRUE),
           q75 = quantile(esc, probs = 0.75, na.rm = TRUE),
           cum_q25 = quantile(cum_esc, probs = 0.25, na.rm = TRUE), 
           cum_q50 = quantile(cum_esc, probs = 0.50, na.rm = TRUE), 
           cum_q75 = quantile(cum_esc, probs = 0.75, na.rm = TRUE)
    ) %>%
    # Always ungroup when you're finished
    ungroup() %>%
    # Deduplicate
    distinct(day_of_year, .keep_all = T) %>% 
    # Remove the helper grouping column
    select(-c(year, esc, date, cum_esc)) 
  
  esc <- left_join(esc_current, esc_hist, by = 'day_of_year') %>% 
    select(-day_of_year)
  
  return(esc)
}

# Apply function to imported escapement data
list2env(lapply(mget(df_names_esc), 
                esc_format), envir = .GlobalEnv)
```

```{r}
#| label: Daily esc plot
#| message: false
#| warning: false
#| include: false

## Daily escapement plot ####

daily_esc_plot <- function(df) {
  
  species <- paste0(substring(sub('.*_', '', deparse(name)), 1, 
             nchar(sub('.*_', '', deparse(name))) -1))
  
  start <-  case_when(species != 'COHO' ~ df[[1,2]],
                      species == 'COHO' ~ df[[round(nrow(df)/3, 0), 2]])
    
  end <- case_when(species == 'SOCKEYE' ~ df[[round(nrow(df)*0.8, 0), 2]],
                   species != 'COHO' ~ df[[round(nrow(df)*0.6, 0), 2]],
                   species == 'COHO' ~ df[[nrow(df), 2]]) 
  
  fill <- case_when(species == 'KING' ~ 'orange',
                    species == 'CHUM' ~ 'lightblue',
                    species == 'PINK' ~ 'pink',
                    species == 'COHO' ~ 'lightgreen',
                    TRUE              ~ 'lightsalmon')
  
  color <- case_when(species == 'KING' ~ 'darkorange',
                    species == 'CHUM' ~ 'darkblue',
                    species == 'PINK' ~ 'maroon',
                    species == 'COHO' ~ 'darkgreen',
                    TRUE              ~ 'lightsalmon4') 
  
  plot <- ggplot() +
  labs(title = paste0(substring(sub('_.*', '', deparse(name)), 2), ' River ', 
                      paste0(str_to_sentence(substring(sub('.*_', '', 
                      deparse(name)), 1, nchar(sub('.*_', '', deparse(name))) -1))), ' Salmon- Daily escapement'), 
       subtitle = paste0('Escapement by date in ', yr),
       caption = 'NOTE: Dashed lines are smoothed 25th, 50th, and 75th historical quartiles',
       x = 'date',
       y = 'escapement') +
  geom_col(data = df, aes(x = date, y = esc), fill = paste0(fill), 
           color = paste0(color)) +
  geom_smooth(data = df, aes(x = date, y = q50, group = year(date)),
              se = F, span = .25, color = 'black', linetype = '12', linewidth = 0.5) +
  geom_smooth(data = df, aes(x = date, y = q25, group = year(date)), 
              se = F, span = .25, color = 'black', linetype = '12', linewidth = 0.5) +
  geom_smooth(data = df, aes(x = date, y = q75, group = year(date)), 
              se = F, span = .25, color = 'black', linetype = '12', linewidth = 0.5) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
  scale_x_date(date_breaks = '5 days', date_labels = '%b %d', 
               limits = as.Date(c(paste0(start), paste0(end))))
  
  return(plot)
}

# Apply fucntion to data
for (name in df_names_esc) {
  # Pull the actual data frame from the environment using its text name
  #current_df <- get(name)
  
  # Run it through the pipeline
  processed_df <- daily_esc_plot(get(name))
  
  # Create the new name (e.g., "df1_plot")
  new_name <- paste0(name, "_daily_plot")
  
  # Save it back into the Global Environment
  assign(new_name, processed_df, envir = .GlobalEnv)
}
```

```{r}
#| label: Cumulative escapement plot
#| echo: false
#| message: false
#| warning: false

# Need a list of rivers with goals
goals <- read.csv('Q:/Salmon/ESCAPEMENT- Salmon/esc_goals.csv')

cum_esc_plot <- function(df) {
  
  name <- substring(deparse(name), 2, nchar(deparse(name)) -1)
  
  species <- paste0(substring(sub('.*_', '', deparse(name)), 1, 
                              nchar(sub('.*_', '', deparse(name))) -1))
  
  river <- paste0(substring(sub('_.*', '', deparse(name)), 2, 
                            nchar(sub('_.*', '', deparse(name)))))
  
  start <-  case_when(species != 'COHO' ~ df[[1,2]],
                      species == 'COHO' ~ df[[round(nrow(df)/3, 0), 2]])
  
  end <- case_when(species == 'SOCKEYE' ~ df[[round(nrow(df)*0.8, 0), 2]],
                   species != 'COHO' ~ df[[round(nrow(df)*0.6, 0), 2]],
                   species == 'COHO' ~ df[[nrow(df), 2]]) 

  
  fill <- case_when(species == 'KING' ~ 'orange',
                    species == 'CHUM' ~ 'lightblue',
                    species == 'PINK' ~ 'pink',
                    species == 'COHO' ~ 'lightgreen',
                    TRUE              ~ 'lightsalmon')
  
  color <- case_when(species == 'KING' ~ 'darkorange',
                     species == 'CHUM' ~ 'darkblue',
                     species == 'PINK' ~ 'maroon',
                     species == 'COHO' ~ 'darkgreen',
                     TRUE              ~ 'lightsalmon4') 
  
  plot <- ggplot() +
    labs(title = paste0(substring(sub('_.*', '', deparse(name)), 2), ' River ', 
                        str_to_sentence(substring(sub('.*_', '', deparse(name)), 1, 
                                                  nchar(sub('.*_', '', deparse(name))) -1)), ' Salmon- Cumulative escapement'), 
         subtitle = paste0('Cumulative escapement in ', yr, ': ', comma(as.integer(df[nrow(df), 'cum_esc'])), 
                           ' fish'),
         caption = 'NOTE: Dashed lines are 25th, 50th, and 75th historical quartiles',
         x = 'date',
         y = 'escapement') +
    # Range goal
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'lower']) == F)
      geom_rect(fill = paste0(fill), alpha = .4, 
                aes(xmin = as.Date(paste0(start)),xmax = as.Date(paste0(end)),
                    ymin = goals[goals$goals == name, 'lower'],
                    ymax = goals[goals$goals == name, 'upper']),
      ) else NULL) +
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'lower']) == F)
      annotate(geom = 'text', hjust = 0, vjust = -0.5, x = as.Date(paste0(start)), y = goals[goals$goals == name, 'lower'],
               label = paste0('Lower goal: ' , comma(as.integer(goals[goals$goals == name, 'lower']))),
      ) else NULL) +
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'upper']) == F)
      annotate(geom = 'text', hjust = 0, vjust = -0.5, x = as.Date(paste0(start)), y = goals[goals$goals == name, 'upper'],
               label = paste0('Upper goal: ' , comma(as.integer(goals[goals$goals == name, 'upper']))),
      ) else NULL) +
    # Point goal
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'point']) == F)
      geom_segment(color = paste0(fill), linewidth = 0.5, linetype = 6,
                   aes(x = as.Date(paste0(start)), xend = as.Date(paste0(end)),
                       y = goals[goals$goals == name, 'point'],
                       yend = goals[goals$goals == name, 'point']),
      ) else NULL) +
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'point']) == F)
      annotate(geom = 'text', hjust = 0, vjust = -0.5, x = as.Date(paste0(start)), y = goals[goals$goals == name, 'point'],
               label = paste0('Goal: ' , comma(as.integer(goals[goals$goals == name, 'point']))),
      ) else NULL) +
    # Pink even year goal
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'even']) == F && yr %% 2 == 0)
      geom_segment(color = paste0(fill), linewidth = 0.5, linetype = 6, 
                   aes(x = as.Date(paste0(start)), xend = as.Date(paste0(end)),
                       y = goals[goals$goals == name, 'even'],
                       yend = goals[goals$goals == name, 'even']),
      ) else NULL) +
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'even']) == F && yr %% 2 == 0)
      annotate(geom = 'text', hjust = 0, vjust = -0.5, x = as.Date(paste0(start)), y = goals[goals$goals == name, 'even'],
               label = paste0('Goal: ' , comma(as.integer(goals[goals$goals == name, 'even']))),
      ) else NULL) +
    # Pink odd year goal
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'odd']) == F && yr %% 2 == 1)
      geom_segment(color = paste0(fill), linewidth = 0.5, linetype = 6,
                   aes(x = as.Date(paste0(start)), xend = as.Date(paste0(end)),
                       y = goals[goals$goals == name, 'odd'],
                       yend = goals[goals$goals == name, 'odd']),
      ) else NULL) +
    (if (name %in% goals$goals && is.na(goals[goals$goals == name, 'odd']) == F && yr %% 2 == 1)
      annotate(geom = 'text', hjust = 0, vjust = -0.5, x = as.Date(paste0(start)), y = goals[goals$goals == name, 'odd'],
               label = paste0('Goal: ' , comma(as.integer(goals[goals$goals == name, 'odd']))),
      ) else NULL) +
    geom_line(data = df, aes(x = date, y = cum_esc), linewidth = 1.25, color = paste0(color)) +
    geom_line(data = df, aes(x = date, y = cum_q50), linewidth = 0.5, linetype = '12') +
    geom_line(data = df, aes(x = date, y = cum_q25), linewidth = 0.5, linetype = '12') +
    geom_line(data = df, aes(x = date, y = cum_q75), linewidth = 0.5, linetype = '12') +
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
    scale_x_date(date_breaks = '5 days', date_labels = '%b %d', 
                 limits = as.Date(c(paste0(start), paste0(end))))
  
  return(plot)
  
}

# Apply function to data
for (name in df_names_esc) {
  # Pull the actual data frame from the environment using its text name
  #current_df <- get(name)
  
  # Run it through the pipeline
  processed_df <- cum_esc_plot(get(name))
  
  # Create the new name (e.g., "df1_plot")
  new_name <- paste0(name, "_cum_plot")
  
  # Save it back into the Global Environment
  assign(new_name, processed_df, envir = .GlobalEnv)
}
```

```{r}
#| label: Commercial data import
#| message: false
#| warning: false
#| include: false

## Import commercial data ####

for (file in list.files(path = paste0('Q:/Salmon/COMMERCIAL- salmon/', yr, ' Commercial'),
                        pattern = '\\.xlsx$', full.names = T)) {
  
  # Get available sheets in the current file to prevent errors
  available_sheets <- excel_sheets(file)
  
  for (sheet in c('KINGS', 'CHUMS', 'SOCKEYES', 'REDS', 'PINKS', 'COHOS')) {
    
    # Check if the specific sheet actually exists in this file
    if (sheet %in% available_sheets) {
      
      # Create a clean, unique variable name (e.g., "df_file1_Sheet1")
      to_remove <- c('333', c(0:60), 'SALMONcatch','_', yr, '.xlsx')
      pattern_regex <- str_c(to_remove, collapse = '|')
      clean_file_name <- str_remove_all(basename(file), pattern_regex)
      var_name <- paste0(clean_file_name, '_', sheet)
      
      # Read the sheet and assign it to its own data frame
      assign(paste0(var_name), read_excel(file, sheet = sheet))
    }
  }
}

# Make a list of data frame names to use for functions 
df_names_comm <- ls(pattern = '^(NOME|ELIM|GOLOVIN|NORTBAY|SHAK|UNK)', envir = .GlobalEnv)
```

```{r}
#| label: Commercial data format
#| message: false
#| warning: false
#| include: false

## Format commercial data ####

comm_format <- function(df) {
  # The first part of this function deletes all unwanted columns and rows
    first_date_col <- df %>%
    select(where(~ any(grepl("date", .x, ignore.case = TRUE)) && 
                   any(grepl("^\\d{5}$", as.character(.x))))) %>%
    select(2) %>%
    colnames()
  # Find year columns by looking for the first valid numerical value
  year_cols_info <- sapply(df, function(col) {
    # Convert everything to numeric; text strings will safely become NA
    suppressWarnings(num_vals <- as.numeric(as.character(col)))
    # Remove all NAs (both original NAs and text that failed to convert)
    clean_nums <- na.omit(num_vals)
    # Skip the column if it contains no numbers at all
    if (length(clean_nums) == 0) return(NA)
    # Grab the first actual number that appeared in the column
    first_num <- clean_nums[1]
    if (first_num >= 1963 && first_num <= yr) {
      return(first_num) # Return the exact year found
    }
    return(NA)
  })
  # Filter out non-matching columns
  valid_year_cols <- year_cols_info[!is.na(year_cols_info)]
  # Keep only the FIRST column name for each unique year found
  unique_year_col_names <- names(valid_year_cols)[!duplicated(valid_year_cols)]
  # Combine the date column with your unique year columns
  final_df <- df %>%
    select(all_of(c(first_date_col, unique_year_col_names)))
  # Convert all selected columns to a numeric matrix to easily search for years
  # (Text and NAs will safely become NA)
  numeric_matrix <- suppressWarnings(
    matrix(as.numeric(as.matrix(final_df)), nrow = nrow(final_df))
  )
    # Find the row indices where any value is between 1963 and current year
  matching_rows <- which(rowSums(numeric_matrix >= 1963 & numeric_matrix <= yr, na.rm = TRUE) > 0)
    # Slice the dataframe starting from the first matching row to the end
  if (length(matching_rows) > 0) {
    first_matching_row <- matching_rows[1]
    final_df_sliced <- final_df %>%
      slice(first_matching_row:n())
  } else {
    # Fallback if no matching row is found (keeps original dataframe)
    final_df_sliced <- final_df 
  }
    final_df_sliced_named <- final_df_sliced %>% 
    set_names(as.character(.[1,])) %>% 
    rename(Date = 1) %>% 
    filter(grepl("^\\d{5}$", as.character(Date))) %>% 
    mutate(across(-1, as.double)) %>% # Make sure everything is numeric
    mutate(Date = as.Date(as.numeric(Date), origin = '1899-12-30')) %>% 
    # Remove all columns with no data- especially in SD1, many years of no fishing
    # can mess up historical averages
    select(paste(yr) | where(~ !all(is.na(.x))))
  
  harv <- final_df_sliced_named %>%
    group_by(Date) %>%
    filter(row_number() == 1) %>%
    ungroup() %>% 
    pivot_longer(cols = !'Date',
                 names_to = 'year',
                 values_to = 'harv') %>%
    mutate(date = make_date(year, month(Date), day(Date))) %>%
    select(-c(Date, year))
  
  permits <- final_df_sliced_named %>%
    group_by(Date) %>%
    filter(row_number() == 3) %>%
    ungroup() %>% 
    pivot_longer(cols = !'Date',
                 names_to = 'year',
                 values_to = 'permits') %>%
    mutate(date = make_date(year, month(Date), day(Date))) %>%
    select(-c(Date, year))
  
  hours <- final_df_sliced_named %>%
    group_by(Date) %>%
    filter(row_number() == 4) %>%
    ungroup() %>% 
    pivot_longer(cols = !'Date',
                 names_to = 'year',
                 values_to = 'hours') %>%
                 mutate(date = make_date(year, month(Date), day(Date))) %>%
                 select(-c(Date, year))
  
# Combine data 
comm_current <- list(harv, hours, permits) %>% 
  reduce(full_join, by = 'date') %>% 
  mutate(across(c(hours, permits, harv), as.numeric),
         cpue = (harv/hours/permits)) %>% 
  filter(year(date) == yr) %>% 
  arrange(date) %>%
  mutate(
    cum_cpue = cumsum(replace_na(cpue, 0)),
    cum_harv = cumsum(replace_na(harv, 0)),
    cum_hours = cumsum(replace_na(hours, 0)),
    day_of_year= format(date, "%m-%d")
  ) 

comm_hist <- list(harv, hours, permits) %>% 
  reduce(full_join, by = 'date') %>% 
  mutate(across(c(hours, permits, harv), as.numeric),
         cpue = (harv/hours/permits)) %>% 
  filter(year(date) != yr) %>% 
  filter(if(grepl('PINKS', deparse(substitute(df))) == TRUE) { 
    year(date) %% 2 == yr %% 2
  } else { TRUE }) %>%
  group_by(year(date)) %>%
  arrange(date) %>%
  mutate(
    cum_cpue = cumsum(replace_na(cpue, 0)),
    cum_harv = cumsum(replace_na(harv, 0)),
    cum_hours = cumsum(replace_na(hours, 0))
  ) %>%
  ungroup() %>% 
  select(-'year(date)') %>% 
  group_by(day_of_year = format(date, "%m-%d")) %>%
  # mutate() adds the new columns while keeping all original rows
  mutate(cpue_q25 = quantile(cpue, probs = 0.25, na.rm = TRUE),
         cpue_q50 = quantile(cpue, probs = 0.50, na.rm = TRUE),
         cpue_q75 = quantile(cpue, probs = 0.75, na.rm = TRUE),
         cum_cpue_q25 = quantile(cum_cpue, probs = 0.25, na.rm = TRUE),
         cum_cpue_q50 = quantile(cum_cpue, probs = 0.50, na.rm = TRUE),
         cum_cpue_q75 = quantile(cum_cpue, probs = 0.75, na.rm = TRUE),
         cum_harv_q25 = quantile(cum_harv, probs = 0.25, na.rm = TRUE),
         cum_harv_q50 = quantile(cum_harv, probs = 0.50, na.rm = TRUE),
         cum_harv_q75 = quantile(cum_harv, probs = 0.75, na.rm = TRUE),
         cum_hours_q25 = quantile(cum_hours, probs = 0.25, na.rm = TRUE),
         cum_hours_q50 = quantile(cum_hours, probs = 0.50, na.rm = TRUE),
         cum_hours_q75 = quantile(cum_hours, probs = 0.75, na.rm = TRUE)
  ) %>%
  ungroup() %>% 
  # Deduplicate
  distinct(day_of_year, .keep_all = T) %>% 
  # Remove helper grouping columns
  select(-c(harv, date, hours, permits, cpue, cum_cpue, cum_harv, cum_hours))

# Combine
comm <- left_join(comm_current, comm_hist, by = 'day_of_year') %>% 
  select(-day_of_year)

rm(comm_current, comm_hist, harv, permits, hours)

return(comm)
}

# Run df_names_comm through the comm_format function
list2env(lapply(mget(df_names_comm), 
                comm_format), envir = .GlobalEnv)
```

```{r}
#| label: CPUE by date plot
#| message: false
#| warning: false
#| include: false

## CPUE by date plot ####

daily_cpue_plot <- function(df) {
  
  species <- paste0(substring(sub('.*_', '', deparse(name)), 1, 
                              nchar(sub('.*_', '', deparse(name))) -2))
  
  start <-  case_when(species != 'COHO' ~ df[[round(nrow(df)/12, 0),2]],
                      species == 'COHO' ~ df[[round(nrow(df)/3, 0), 2]])
  
  end <- case_when(species == 'SOCKEYE' ~ df[[round(nrow(df)*0.8, 0), 2]],
                   species != 'COHO' ~ df[[round(nrow(df)*0.6, 0), 2]],
                   species == 'COHO' ~ df[[round(nrow(df)*0.9, 0), 2]]) 
  
  fill <- case_when(species == 'KING' ~ 'orange',
                    species == 'CHUM' ~ 'lightblue',
                    species == 'PINK' ~ 'pink',
                    species == 'COHO' ~ 'lightgreen',
                    TRUE              ~ 'lightsalmon')
  
  color <- case_when(species == 'KING' ~ 'darkorange',
                     species == 'CHUM' ~ 'darkblue',
                     species == 'PINK' ~ 'maroon',
                     species == 'COHO' ~ 'darkgreen',
                     TRUE              ~ 'lightsalmon4') 
  
  sd_code <- paste0(substring(sub('_.*', '', deparse(name)), 2))
  
  sd <- case_when(sd_code == 'NOME' ~ 'Nome',
                  sd_code == 'ELIM' ~ 'Elim',
                  sd_code == 'GOLOVIN' ~ 'Golovin',
                  sd_code == 'NORTBAY' ~ 'Norton Bay',
                  sd_code == 'SHAK' ~ 'Shaktoolik',
                  sd_code == 'UNK' ~ 'Unalakleet')
  
  plot <- ggplot() +
    labs(title = paste0(sd, ' Subdistrict ', 
                        paste0(str_to_sentence(substring(sub('.*_', '', 
                        deparse(name)), 1, nchar(sub('.*_', '', deparse(name))) -2))), ' Salmon- CPUE by date'), 
         subtitle = paste0('CPUE by date in ', yr),
         caption = 'NOTE: Dashed lines are smoothed 25th, 50th, and 75th historical quartiles',
         x = 'date',
         y = 'cpue') +
    geom_smooth(data = df, aes(x = date, y = cpue_q25, group = year(date)),
                se = F, span = .25, color = 'black', linetype = '12', linewidth = 0.5) +
    geom_smooth(data = df, aes(x = date, y = cpue_q50, group = year(date)), 
                se = F, span = .25, color = 'black', linetype = '12', linewidth = 0.5) +
    geom_smooth(data = df, aes(x = date, y = cpue_q75, group = year(date)), 
                se = F, span = .25, color = 'black', linetype = '12', linewidth = 0.5) +
    geom_point(data = df, aes(x = date, y = cpue), size = 2.5, color = paste0(color)) +
    geom_label(data = df, aes(x = date, y = cpue, label = round(cpue, 2)), 
               vjust = -1, size = 3.5) +
    coord_cartesian(clip = "off") +
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
    scale_x_date(date_breaks = '5 days', date_labels = '%b %d', 
                 limits = as.Date(c(paste0(start), paste0(end))))
  
  return(plot)
}

# Apply function to data
for (name in df_names_comm) {
  # Pull the actual data frame from the environment using its text name
  #current_df <- get(name)
  
  # Run it through the pipeline
  processed_df <- daily_cpue_plot(get(name))
  
  # Create the new name (e.g., "df1_plot")
  new_name <- paste0(name, "_daily_cpue_plot")
  
  # Save it back into the Global Environment
  assign(new_name, processed_df, envir = .GlobalEnv)
}
```

```{r}
#| label: Cum CPUE plot
#| message: false
#| warning: false
#| include: false
## Cumulative CPUE plot template ####

cum_cpue_plot <- function(df) {
  
  species <- paste0(substring(sub('.*_', '', deparse(name)), 1, 
                              nchar(sub('.*_', '', deparse(name))) -2))
  
  start <-  case_when(species != 'COHO' ~ df[[round(nrow(df)/12, 0),2]],
                      species == 'COHO' ~ df[[round(nrow(df)/3, 0), 2]])
  
  end <- case_when(species == 'SOCKEYE' ~ df[[round(nrow(df)*0.8, 0), 2]],
                   species != 'COHO' ~ df[[round(nrow(df)*0.6, 0), 2]],
                   species == 'COHO' ~ df[[round(nrow(df)*0.9, 0), 2]]) 
  
  fill <- case_when(species == 'KING' ~ 'orange',
                    species == 'CHUM' ~ 'lightblue',
                    species == 'PINK' ~ 'pink',
                    species == 'COHO' ~ 'lightgreen',
                    TRUE              ~ 'lightsalmon')
  
  color <- case_when(species == 'KING' ~ 'darkorange',
                     species == 'CHUM' ~ 'darkblue',
                     species == 'PINK' ~ 'maroon',
                     species == 'COHO' ~ 'darkgreen',
                     TRUE              ~ 'lightsalmon4') 
  
  sd_code <- paste0(substring(sub('_.*', '', deparse(name)), 2))
  
  sd <- case_when(sd_code == 'NOME' ~ 'Nome',
                  sd_code == 'ELIM' ~ 'Elim',
                  sd_code == 'GOLOVIN' ~ 'Golovin',
                  sd_code == 'NORTBAY' ~ 'Norton Bay',
                  sd_code == 'SHAK' ~ 'Shaktoolik',
                  sd_code == 'UNK' ~ 'Unalakleet')
  
  plot <- ggplot() +
    labs(title = paste0(sd, ' Subdistrict ', 
                        paste0(str_to_sentence(substring(sub('.*_', '', 
                        deparse(name)), 1, nchar(sub('.*_', '', deparse(name))) -2))), ' Salmon- Cumulative CPUE'), 
         subtitle = paste0('Cumulative CPUE in ', yr, ': ', round(df[nrow(df), 'cum_cpue'], 2)),
         caption = 'NOTE: Dashed lines are 25th, 50th, and 75th historical quartiles',
         x = 'date',
         y = 'cpue') +
    geom_line(data = df, aes(x = date, y = cum_cpue_q25, group = year(date)),
                color = 'black', linetype = '12',
                linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_cpue_q50, group = year(date)), 
                color = 'black', linetype = '12',
                linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_cpue_q75, group = year(date)), 
                color = 'black', linetype = '12',
                linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_cpue), color = paste0(color),
              linewidth = 1.25) +
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
    scale_x_date(date_breaks = '5 days', date_labels = '%b %d', 
                 limits = as.Date(c(paste0(start), paste0(end))))
  
  return(plot)
}

# Apply function to data
for (name in df_names_comm) {
  # Pull the actual data frame from the environment using its text name
  #current_df <- get(name)
  
  # Run it through the pipeline
  processed_df <- cum_cpue_plot(get(name))
  
  # Create the new name (e.g., "df1_plot")
  new_name <- paste0(name, "_cum_cpue_plot")
  
  # Save it back into the Global Environment
  assign(new_name, processed_df, envir = .GlobalEnv)
}
```

```{r}
#| label: Cum harv plot
#| message: false
#| warning: false
#| include: false
## Cumulative harvest plot template ####

cum_harv_plot <- function(df) {
  
  species <- paste0(substring(sub('.*_', '', deparse(name)), 1, 
                              nchar(sub('.*_', '', deparse(name))) -2))
  
  start <-  case_when(species != 'COHO' ~ df[[round(nrow(df)/12, 0),2]],
                      species == 'COHO' ~ df[[round(nrow(df)/3, 0), 2]])
  
  end <- case_when(species == 'SOCKEYE' ~ df[[round(nrow(df)*0.8, 0), 2]],
                   species != 'COHO' ~ df[[round(nrow(df)*0.6, 0), 2]],
                   species == 'COHO' ~ df[[round(nrow(df)*0.9, 0), 2]]) 
  
  fill <- case_when(species == 'KING' ~ 'orange',
                    species == 'CHUM' ~ 'lightblue',
                    species == 'PINK' ~ 'pink',
                    species == 'COHO' ~ 'lightgreen',
                    TRUE              ~ 'lightsalmon')
  
  color <- case_when(species == 'KING' ~ 'darkorange',
                     species == 'CHUM' ~ 'darkblue',
                     species == 'PINK' ~ 'maroon',
                     species == 'COHO' ~ 'darkgreen',
                     TRUE              ~ 'lightsalmon4') 
  
  sd_code <- paste0(substring(sub('_.*', '', deparse(name)), 2))
  
  sd <- case_when(sd_code == 'NOME' ~ 'Nome',
                  sd_code == 'ELIM' ~ 'Elim',
                  sd_code == 'GOLOVIN' ~ 'Golovin',
                  sd_code == 'NORTBAY' ~ 'Norton Bay',
                  sd_code == 'SHAK' ~ 'Shaktoolik',
                  sd_code == 'UNK' ~ 'Unalakleet')
  
  plot <- ggplot() +
  labs(title = paste0(sd, ' Subdistrict ', 
                      paste0(str_to_sentence(substring(sub('.*_', '', 
                      deparse(name)), 1, nchar(sub('.*_', '', deparse(name))) -2))), ' Salmon- Cumulative harvest'),
       subtitle = paste0('Cumulative harvest in ', yr, ': ', comma(as.integer(df[nrow(df), 'cum_harv']))),
       caption = 'NOTE: Dashed lines are 25th, 50th, and 75th historical quartiles',
       x = 'date',
       y = 'harvest') +
    geom_line(data = df, aes(x = date, y = cum_harv_q25, group = year(date)),
                color = 'black', linetype = '12',
                linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_harv_q50, group = year(date)), 
                color = 'black', linetype = '12',
                linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_harv_q75, group = year(date)), 
                color = 'black', linetype = '12',
                linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_harv), color = paste0(color),
              linewidth = 1.25) +
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
    scale_x_date(date_breaks = '5 days', date_labels = '%b %d', 
                 limits = as.Date(c(paste0(start), paste0(end))))
  
  return(plot)
}

for (name in df_names_comm) {
  # Pull the actual data frame from the environment using its text name
  #current_df <- get(name)
  
  # Run it through the pipeline
  processed_df <- cum_harv_plot(get(name))
  
  # Create the new name (e.g., "df1_plot")
  new_name <- paste0(name, "_cum_harv_plot")
  
  # Save it back into the Global Environment
  assign(new_name, processed_df, envir = .GlobalEnv)
}
```

```{r}
#| label: Cum hours plot
#| message: false
#| warning: false
#| include: false
## Cumulative hours plot template ####


cum_hours_plot <- function(df) {
  
  start <-  df[[1,2]]
  
  end <- df[[nrow(df), 2]] 
  
  color <- 'firebrick'
  
  sd_code <- paste0(substring(sub('_.*', '', deparse(name)), 2))
  
  sd <- case_when(sd_code == 'NOME' ~ 'Nome',
                  sd_code == 'ELIM' ~ 'Elim',
                  sd_code == 'GOLOVIN' ~ 'Golovin',
                  sd_code == 'NORTBAY' ~ 'Norton Bay',
                  sd_code == 'SHAK' ~ 'Shaktoolik',
                  sd_code == 'UNK' ~ 'Unalakleet')
  
  plot <- ggplot() +
    labs(title = paste0(sd, ' Subdistrict- Commercial fishing hours'), 
         subtitle = paste0('Cumulative fishing hours in ', yr, ': ', round(df[nrow(df), 'cum_hours'], 2)),
         caption = 'NOTE: Dashed lines are smoothed 25th, 50th, and 75th historical quartiles',
         x = 'date',
         y = 'hours') +
    geom_line(data = df, aes(x = date, y = cum_hours_q25, group = year(date)),
              color = 'black', linetype = '12',
              linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_hours_q50, group = year(date)), 
              color = 'black', linetype = '12',
              linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_hours_q75, group = year(date)), 
              color = 'black', linetype = '12',
              linewidth = 0.5) +
    geom_line(data = df, aes(x = date, y = cum_hours), color = paste0(color),
              linewidth = 1.25) +
    theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1)) +
    scale_x_date(date_breaks = '7 days', date_labels = '%b %d', 
                 limits = as.Date(c(paste0(start), paste0(end))))
  
  return(plot)
}

for (name in df_names_comm[grepl('CHUM', df_names_comm)]) {
  # Doesn't matter the species since it is the same commercial hours for all
  
  # Run it through the pipeline
  processed_df <- cum_hours_plot(get(name))
  
  # Create the new name (e.g., "df1_plot")
  new_name <- paste0(paste0(substring(sub('_.*', '', deparse(name)), 2)), "_cum_hours_plot")
  
  # Save it back into the Global Environment
  assign(new_name, processed_df, envir = .GlobalEnv)
}
```

# Subdistrict 1- Nome

## Nome Subdistrict Escapement

### Snake River weir

```{r}
#| label: Snake weir
#| echo: false
#| message: false
#| warning: false
Snake_KING_daily_plot
Snake_KING_cum_plot
Snake_CHUM_daily_plot
Snake_CHUM_cum_plot
Snake_PINK_daily_plot
Snake_PINK_cum_plot
Snake_SOCKEYE_daily_plot
Snake_SOCKEYE_cum_plot
Snake_COHO_daily_plot
Snake_COHO_cum_plot
```

### Nome River weir

```{r}
#| label: Nome weir
#| echo: false
#| message: false
#| warning: false
Nome_KING_daily_plot
Nome_KING_cum_plot
Nome_CHUM_daily_plot
Nome_CHUM_cum_plot
Nome_PINK_daily_plot
Nome_PINK_cum_plot
Nome_SOCKEYE_daily_plot
Nome_SOCKEYE_cum_plot
Nome_COHO_daily_plot
Nome_COHO_cum_plot
```

### Eldorado River weir

```{r}
#| label: Eldo weir
#| echo: false
#| message: false
#| warning: false
Eldorado_KING_daily_plot
Eldorado_KING_cum_plot
Eldorado_CHUM_daily_plot
Eldorado_CHUM_cum_plot
Eldorado_PINK_daily_plot
Eldorado_PINK_cum_plot
Eldorado_SOCKEYE_daily_plot
Eldorado_SOCKEYE_cum_plot
Eldorado_COHO_daily_plot
Eldorado_COHO_cum_plot
```

## Nome Subdistrict Commercial Harvest

```{r}
#| label: SD1 comm harvest
#| echo: false
#| message: false
#| warning: false

NOME_cum_hours_plot

NOME_KINGS_daily_cpue_plot
NOME_KINGS_cum_cpue_plot
NOME_KINGS_cum_harv_plot

NOME_CHUMS_daily_cpue_plot
NOME_CHUMS_cum_cpue_plot
NOME_CHUMS_cum_harv_plot

NOME_PINKS_daily_cpue_plot
NOME_PINKS_cum_cpue_plot
NOME_PINKS_cum_harv_plot

NOME_REDS_daily_cpue_plot
NOME_REDS_cum_cpue_plot
NOME_REDS_cum_harv_plot

NOME_COHOS_daily_cpue_plot
NOME_COHOS_cum_cpue_plot
NOME_COHOS_cum_harv_plot
```

# Subdistrict 2- Golovin

## Golovin Subdistrict Escapement

### Niukluk River weir

```{r}
#| label: Niukluk weir
#| echo: false
#| message: false
#| warning: false
Niukluk_KING_daily_plot
Niukluk_KING_cum_plot
Niukluk_CHUM_daily_plot
Niukluk_CHUM_cum_plot
Niukluk_PINK_daily_plot
Niukluk_PINK_cum_plot
Niukluk_COHO_daily_plot
Niukluk_COHO_cum_plot
```

## Golovin Subdistrict Commercial Harvest

```{r}
#| label: SD2 comm harvest
#| echo: false
#| message: false
#| warning: false

GOLOVIN_cum_hours_plot

GOLOVIN_KINGS_daily_cpue_plot
GOLOVIN_KINGS_cum_cpue_plot
GOLOVIN_KINGS_cum_harv_plot

GOLOVIN_CHUMS_daily_cpue_plot
GOLOVIN_CHUMS_cum_cpue_plot
GOLOVIN_CHUMS_cum_harv_plot

GOLOVIN_PINKS_daily_cpue_plot
GOLOVIN_PINKS_cum_cpue_plot
GOLOVIN_PINKS_cum_harv_plot

GOLOVIN_REDS_daily_cpue_plot
GOLOVIN_REDS_cum_cpue_plot
GOLOVIN_REDS_cum_harv_plot

GOLOVIN_COHOS_daily_cpue_plot
GOLOVIN_COHOS_cum_cpue_plot
GOLOVIN_COHOS_cum_harv_plot
```

# Subdistrict 3- Elim

## Elim Subdistrict Escapement

### Kwiniuk River tower

```{r}
#| label: Kwiniuk tower
#| echo: false
#| message: false
#| warning: false
Kwiniuk_KING_daily_plot
Kwiniuk_KING_cum_plot
Kwiniuk_CHUM_daily_plot
Kwiniuk_CHUM_cum_plot
Kwiniuk_PINK_daily_plot
Kwiniuk_PINK_cum_plot
Kwiniuk_COHO_daily_plot
Kwiniuk_COHO_cum_plot
```

## Elim Subdistrict Commercial Harvest

```{r}
#| label: SD3 comm harvest
#| echo: false
#| message: false
#| warning: false

ELIM_cum_hours_plot

ELIM_KINGS_daily_cpue_plot
ELIM_KINGS_cum_cpue_plot
ELIM_KINGS_cum_harv_plot

ELIM_CHUMS_daily_cpue_plot
ELIM_CHUMS_cum_cpue_plot
ELIM_CHUMS_cum_harv_plot

ELIM_PINKS_daily_cpue_plot
ELIM_PINKS_cum_cpue_plot
ELIM_PINKS_cum_harv_plot

ELIM_REDS_daily_cpue_plot
ELIM_REDS_cum_cpue_plot
ELIM_REDS_cum_harv_plot

ELIM_COHOS_daily_cpue_plot
ELIM_COHOS_cum_cpue_plot
ELIM_COHOS_cum_harv_plot
```

# Subdistrict 4- Norton Bay

## Norton Bay Subdistrict Escapement

### Ungalik River tower

```{r}
#| label: Ungalik tower
#| echo: false
#| message: false
#| warning: false
Ungalik_KING_daily_plot
Ungalik_KING_cum_plot
Ungalik_CHUM_daily_plot
Ungalik_CHUM_cum_plot
Ungalik_PINK_daily_plot
Ungalik_PINK_cum_plot
Ungalik_COHO_daily_plot
Ungalik_COHO_cum_plot
```

## Norton Bay Subdistrict Commercial Harvest

```{r}
#| label: SD4 comm harvest
#| echo: false
#| message: false
#| warning: false

NORTBAY_cum_hours_plot

NORTBAY_KINGS_daily_cpue_plot
NORTBAY_KINGS_cum_cpue_plot
NORTBAY_KINGS_cum_harv_plot

NORTBAY_CHUMS_daily_cpue_plot
NORTBAY_CHUMS_cum_cpue_plot
NORTBAY_CHUMS_cum_harv_plot

NORTBAY_PINKS_daily_cpue_plot
NORTBAY_PINKS_cum_cpue_plot
NORTBAY_PINKS_cum_harv_plot

NORTBAY_REDS_daily_cpue_plot
NORTBAY_REDS_cum_cpue_plot
NORTBAY_REDS_cum_harv_plot

NORTBAY_COHOS_daily_cpue_plot
NORTBAY_COHOS_cum_cpue_plot
NORTBAY_COHOS_cum_harv_plot
```

# Subdistrict 5- Shaktoolik

## Shaktoolik Subdistrict Escapement

### Shaktoolik River tower

```{r}
#| label: Shaktoolik tower
#| echo: false
#| message: false
#| warning: false
Shaktoolik_KING_daily_plot
Shaktoolik_KING_cum_plot
Shaktoolik_CHUM_daily_plot
Shaktoolik_CHUM_cum_plot
Shaktoolik_PINK_daily_plot
Shaktoolik_PINK_cum_plot
Shaktoolik_COHO_daily_plot
Shaktoolik_COHO_cum_plot
```

## Shaktoolik Subdistrict Commercial Harvest

```{r}
#| label: SD5 comm harvest
#| echo: false
#| message: false
#| warning: false

SHAK_cum_hours_plot

SHAK_KINGS_daily_cpue_plot
SHAK_KINGS_cum_cpue_plot
SHAK_KINGS_cum_harv_plot

SHAK_CHUMS_daily_cpue_plot
SHAK_CHUMS_cum_cpue_plot
SHAK_CHUMS_cum_harv_plot

SHAK_PINKS_daily_cpue_plot
SHAK_PINKS_cum_cpue_plot
SHAK_PINKS_cum_harv_plot

SHAK_REDS_daily_cpue_plot
SHAK_REDS_cum_cpue_plot
SHAK_REDS_cum_harv_plot

SHAK_COHOS_daily_cpue_plot
SHAK_COHOS_cum_cpue_plot
SHAK_COHOS_cum_harv_plot
```

# Subdistrict 6- Unalakleet

## Unalakleet Subdistrict Escapement

### North River tower

```{r}
#| label: North tower
#| echo: false
#| message: false
#| warning: false
North_KING_daily_plot
North_KING_cum_plot
North_CHUM_daily_plot
North_CHUM_cum_plot
North_PINK_daily_plot
North_PINK_cum_plot
North_COHO_daily_plot
North_COHO_cum_plot
```

## Unalakleet Subdistrict Commercial Harvest

```{r}
#| label: SD6 comm harvest
#| echo: false
#| message: false
#| warning: false

UNK_cum_hours_plot

UNK_KINGS_daily_cpue_plot
UNK_KINGS_cum_cpue_plot
UNK_KINGS_cum_harv_plot

UNK_CHUMS_daily_cpue_plot
UNK_CHUMS_cum_cpue_plot
UNK_CHUMS_cum_harv_plot

UNK_PINKS_daily_cpue_plot
UNK_PINKS_cum_cpue_plot
UNK_PINKS_cum_harv_plot

UNK_REDS_daily_cpue_plot
UNK_REDS_cum_cpue_plot
UNK_REDS_cum_harv_plot

UNK_COHOS_daily_cpue_plot
UNK_COHOS_cum_cpue_plot
UNK_COHOS_cum_harv_plot
```
